---
title: "Practicle machine learning Final Assignment "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data
The training data for this project are available here:
[link]https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv
The test data are available here:
[link]https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv
The data for this project come from this source: [link]http://groupware.les.inf.puc-rio.br/har. If you use the document you create for this class for any purpose please cite them as they have been very generous in allowing their data to be used for this kind of assignment.


##What you should submit
The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. You may use any of the other variables to predict with. You should create a report describing how you built your model, how you used cross validation, what you think the expected out of sample error is, and why you made the choices you did. You will also use your prediction model to predict 20 different test cases.

### Packages

```{r library}
# require package caret, rattle
library(caret)
library(rattle)	
```

### Get data and clean data

```{r get data}
raw_training<-read.csv('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv',na.strings=c("NA","#DIV/0!", ""))
raw_testing<-read.csv('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv',na.strings=c("NA","#DIV/0!", ""))
set.seed(323)
## Remove NA
train<-raw_training[,colSums(is.na(raw_training)) == 0]
test <-raw_testing[,colSums(is.na(raw_testing)) == 0]

## Not every variable is predictors, delete those irrevelent
train_final<-train[,-c(1:7)]
test_final<-test[,-c(1:7)]

## Subset the data for evaluate the performance of different classifiers
division<-createDataPartition(y=train_final$classe, p=0.70, list=FALSE)
subtrain<-train_final[division,]
validation<-train_final[-division,]
dim(subtrain)
dim(validation)
dim(test)

```
## Different classifiers by different methods
1. By using the rpart, treebag and rf methods in caret packages
2. Compare their performance
3. Majorly forcast in decision tree methods

### Tree by rpart
```{r rpart}
#caret rpart
model_tree1 <-train(classe~.,data=subtrain,method="rpart",tuneLength=20,trControl=trainControl(method="cv", number=10))
fancyRpartPlot(model_tree1$finalModel)
pred_tree1<-predict(model_tree1,newdata=validation,type="raw")
confusionMatrix(pred_tree1,validation$classe)

```
### Bagging the tree
* The accuracy of rpart is 0.77, what if bagging the tree?

```{r treebag}
model_tree2 <-train(classe~.,data=subtrain,method="treebag",tuneLength=20,trControl=trainControl(method="cv", number=10))
pred_tree2<-predict(model_tree2,newdata=validation,type="raw")
confusionMatrix(pred_tree2,validation$classe)

```

### Random forest
* The accuracy of bagging the tree is increasing, what if bagging the tree as random forest?

```{r random forest}
model_rf <-train(classe~.,data=subtrain,method="rf",trControl=trainControl(method="cv", number=10))
pred_rf<-predict(model_rf,newdata=validation,type="raw")
confusionMatrix(pred_rf,validation$classe)
# importance of each predictor
importance(model_rf)
```
### Prediction of test set
* Apply the best performance classifier (_modelrf_) into the test set
```{r prediction}
pred_test<-predict(model_rf,newdata=test_final,type="raw")
print(pred_test)
```

